---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# petroOne

The goal of petroOne is to ...

## Installation

You can install petroOne from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("f0nzie/petroOne")
```

## Examples

### Get the number of papers for *neural networks*.

```{r example}
library(petroOne)

my_url <- make_search_url(query = "neural network", how = "any")
my_url
get_papers_count(my_url)
# 3284
# 3314
```

### Read papers from from_year to to_year
We can send a query where we specify the starting years and the end year.
Use the parameters as in the example below.

```{r}
library(petroOne)

# neural network papers from 1990 to 2000. Exact phrase
my_url <- make_search_url(query = "neural network", 
                          from_year = 1990, 
                          to_year   = 1999, 
                          how = "all")

get_papers_count(my_url)
# 415
# 510
onepetro_page_to_dataframe(my_url)
```

## Get papers by document type (dc_type)
We can also get paper by the type of document.
In this example we are requesting only "conference-paper" type.

```{r}
# specify document type = "conference-paper", rows = 1000

my_url <- make_search_url(query = "neural network", 
                          how = "all",
                          dc_type = "conference-paper",
                          rows = 1000)

get_papers_count(my_url)
# 2661
# 2687
onepetro_page_to_dataframe(my_url)
```

In this other example we are requesting for "journal-paper" type of papers.

```{r}
# specify document type = "journal-paper", rows = 1000

my_url <- make_search_url(query = "neural network", 
                          how = "all",
                          dc_type = "journal-paper",
                          rows = 1000)

get_papers_count(my_url)
# 303
# 304
onepetro_page_to_dataframe(my_url)
```

## What to do when we have more than a thousand papers

### 1. Get total number of papers
First, we need to find what is the total number of papers for a particular query.
In this search we want all papers that have exact words "neural network".


```{r}

my_url <- make_search_url(query = "neural network", 
                          how = "all")

get_papers_count(my_url)
# 3025 @ 200171009   total number of papers
```

### 2. Find type of papers
In this example we investigate the type of papers available for a given search.
In this case, we want exact match of "neural network" words.

```{r}
result <- read_onepetro(my_url)
summary_by_doctype(result)
```

We see that most numerous papers are from conferences. We will proceed to gran the paper titles of those.


## Summaries
Here is a nother example of summaries.
In this case, we want papers that contain the exact words "well test".

```{r}
library(petroOne)

my_url <- make_search_url(query = "well test", 
                          how = "all")

result <- read_onepetro(my_url)

summary_by_doctype(result)
summary_by_publisher(result)
summary_by_dates(result)
summary_by_publications(result)
```


In this other example, we want papers that containg the word "well" or "test".

```{r}
library(petroOne)

my_url <- make_search_url(query = "well test", 
                          how = "any")

result <- read_onepetro(my_url)

summary_by_doctype(result)
summary_by_publisher(result)
summary_by_dates(result)
summary_by_publications(result)
```

